---
title: "Ovsanna"
author: "Hsueh-Pin Liu, Nuo Chen, Tao Guo, Huifei Xu"
date: "`r Sys.Date()`"
output: 
    pdf_document:
        latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Our client, Ovsanna Leyfer, who is from Psychological and Brain Sciences Department, want to develop an intensive (delivered over a course of one week) intervention to deliver CBT for youth aged 11-17 with ANY anxiety disorder to reduce the disability and impairment associated with anxiety disorders. Therefore, She created a multiple baseline study looking at treatment outcomes where eight participants were randomized to 2, 3, or 4 week baseline before starting a one-week treatment, and were asked to answer self-assessment questions every day during the pre-treatment and post-treatment. Our team's goal is to examine the potential indicators of treatment efficacy, as well as to give some statistical insights.


## Previous steps

Before making the EDAs, We first changed the variable's names of the .xlsx file to make it easier to import, so the new .xlsx file is different from the original one.

```{r include=F}
library(ggplot2)
library(readxl)
library(tidyverse)
library(ggpubr)
library(lmerTest)
library(stats)
library(ordinal)
library(nlme)
library(dplyr)
data<- read_excel("Daily Monitor Tracking Log.xlsx")
```


# EDAs

According to the data, there are 2 "two-week" patients, 4"three-week" patients and 2 "four-week" patients. We make plots for each patient's each question and the black line seperates the pre-treatment and treatment time.

```{r Fig1, fig.cap="2-week pre-treatment patients",echo=F,warning=F,fig.height=4,fig.width=10}
#Two weeks
#1
data1 <- data[c(1:8),]
data1 <- data1[, colSums(is.na(data1)) != nrow(data1)]
data1 <- data1[,-c(1:3)]
x <- rep(NA,8)
data1 <- cbind(data1[,c(1:14)], x, data1[,c(15:22)])
Time <- rep(c("W1D1","W1D2","W1D3","W1D4","W1D5","W1D6","W1D7","W2D1","W2D2","W2D3","W2D4","W2D5","W2D6","W2D7","Split","TrD1","TrD2","TrD3","TrD4","TrD5","TrD6","TrD7","TrD8"),8)
Score <- c(t(as.matrix(data1)))
Question <- rep(c("Question1","Question2","Question3","Question4","Question5","Question6","Question7","Question8"),each=23)
df <- data.frame(Time=Time,Score=Score,Question=Question)
df$Time <- factor(df$Time,levels=c("W1D1","W1D2","W1D3","W1D4","W1D5","W1D6","W1D7","W2D1","W2D2","W2D3","W2D4","W2D5","W2D6","W2D7","Split","TrD1","TrD2","TrD3","TrD4","TrD5","TrD6","TrD7","TrD8"))
p1 <- ggplot(data=df,mapping=aes(x=Time,y=Score,group=Question,colour=Question))+geom_line()+geom_point()+theme(axis.text.x=element_blank())+scale_y_continuous(limits = c(0, 8))+ggtitle("ID=1, Randomization=2")+facet_wrap(~Question)+geom_vline(xintercept=15)

#2

data2 <- data[c(17:24),]
data2 <- data2[, colSums(is.na(data2)) != nrow(data2)]
data2 <- data2[,-c(1:3)]
x <- rep(NA,8)
data2 <- cbind(data2[,c(1:14)], x, data2[,c(15:22)])
Time <- rep(c("W1D1","W1D2","W1D3","W1D4","W1D5","W1D6","W1D7","W2D1","W2D2","W2D3","W2D4","W2D5","W2D6","W2D7","Split","TrD1","TrD2","TrD3","TrD4","TrD5","TrD6","TrD7","TrD8"),8)
Score <- c(t(as.matrix(data2)))
Question <- rep(c("Question1","Question2","Question3","Question4","Question5","Question6","Question7","Question8"),each=23)
df <- data.frame(Time=Time,Score=Score,Question=Question)
df$Time <- factor(df$Time,levels=c("W1D1","W1D2","W1D3","W1D4","W1D5","W1D6","W1D7","W2D1","W2D2","W2D3","W2D4","W2D5","W2D6","W2D7","Split","TrD1","TrD2","TrD3","TrD4","TrD5","TrD6","TrD7","TrD8"))
p2 <- ggplot(data=df,mapping=aes(x=Time,y=Score,group=Question,colour=Question))+geom_line()+geom_point()+theme(axis.text.x=element_blank())+scale_y_continuous(limits = c(0, 8))+ggtitle("ID=3, Randomization=2")+facet_wrap(~Question)+geom_vline(xintercept=15)
ggarrange(p1,p2,ncol=2,nrow=1)
```

```{r Fig2, fig.cap="3-week pre-treatment patients",echo=F,warning=F,fig.height=8,fig.width=10}
#Three weeks
#3
data3 <- data[c(9:16),]
data3 <- data3[, colSums(is.na(data3)) != nrow(data3)]
data3 <- data3[,-c(1:3)]
x <- rep(NA,8)
data3 <- cbind(data3[,c(1:21)], x, data3[,c(22:29)])
Time <- rep(c("W1D1","W1D2","W1D3","W1D4","W1D5","W1D6","W1D7","W2D1","W2D2","W2D3","W2D4","W2D5","W2D6","W2D7","W3D1","W3D2","W3D3","W3D4","W3D5","W3D6","W3D7","Split","TrD1","TrD2","TrD3","TrD4","TrD5","TrD6","TrD7","TrD8"),8)
Score <- c(t(as.matrix(data3)))
Question <- rep(c("Question1","Question2","Question3","Question4","Question5","Question6","Question7","Question8"),each=30)
df <- data.frame(Time=Time,Score=Score,Question=Question)
df$Time <- factor(df$Time,levels=c("W1D1","W1D2","W1D3","W1D4","W1D5","W1D6","W1D7","W2D1","W2D2","W2D3","W2D4","W2D5","W2D6","W2D7","W3D1","W3D2","W3D3","W3D4","W3D5","W3D6","W3D7","Split","TrD1","TrD2","TrD3","TrD4","TrD5","TrD6","TrD7","TrD8"))
p3 <- ggplot(data=df,mapping=aes(x=Time,y=Score,group=Question,colour=Question))+geom_line()+geom_point()+theme(axis.text.x=element_blank())+scale_y_continuous(limits = c(0, 8))+ggtitle("ID=5, Randomization=3")+facet_wrap(~Question)+geom_vline(xintercept=22)

#4
data4 <- data[c(33:40),]
data4 <- data4[, colSums(is.na(data4)) != nrow(data4)]
data4 <- data4[,-c(1:3)]
x <- rep(NA,8)
data4 <- cbind(data4[,c(1:21)], x, data4[,c(22:29)])
Time <- rep(c("W1D1","W1D2","W1D3","W1D4","W1D5","W1D6","W1D7","W2D1","W2D2","W2D3","W2D4","W2D5","W2D6","W2D7","W3D1","W3D2","W3D3","W3D4","W3D5","W3D6","W3D7","Split","TrD1","TrD2","TrD3","TrD4","TrD5","TrD6","TrD7","TrD8"),8)
Score <- c(t(as.matrix(data4)))
Question <- rep(c("Question1","Question2","Question3","Question4","Question5","Question6","Question7","Question8"),each=30)
df <- data.frame(Time=Time,Score=Score,Question=Question)
df$Time <- factor(df$Time,levels=c("W1D1","W1D2","W1D3","W1D4","W1D5","W1D6","W1D7","W2D1","W2D2","W2D3","W2D4","W2D5","W2D6","W2D7","W3D1","W3D2","W3D3","W3D4","W3D5","W3D6","W3D7","Split","TrD1","TrD2","TrD3","TrD4","TrD5","TrD6","TrD7","TrD8"))
p4 <- ggplot(data=df,mapping=aes(x=Time,y=Score,group=Question,colour=Question))+geom_line()+geom_point()+theme(axis.text.x=element_blank())+scale_y_continuous(limits = c(0, 8))+ggtitle("ID=9, Randomization=3")+facet_wrap(~Question)+geom_vline(xintercept=22)

#5
data5 <- data[c(41:48),]
data5 <- data5[, colSums(is.na(data5)) != nrow(data5)]
data5 <- data5[,-c(1:3)]
x <- rep(NA,8)
data5 <- cbind(data5[,c(1:21)], x, data5[,c(22:29)])
Time <- rep(c("W1D1","W1D2","W1D3","W1D4","W1D5","W1D6","W1D7","W2D1","W2D2","W2D3","W2D4","W2D5","W2D6","W2D7","W3D1","W3D2","W3D3","W3D4","W3D5","W3D6","W3D7","Split","TrD1","TrD2","TrD3","TrD4","TrD5","TrD6","TrD7","TrD8"),8)
Score <- c(t(as.matrix(data5)))
Question <- rep(c("Question1","Question2","Question3","Question4","Question5","Question6","Question7","Question8"),each=30)
df <- data.frame(Time=Time,Score=Score,Question=Question)
df$Time <- factor(df$Time,levels=c("W1D1","W1D2","W1D3","W1D4","W1D5","W1D6","W1D7","W2D1","W2D2","W2D3","W2D4","W2D5","W2D6","W2D7","W3D1","W3D2","W3D3","W3D4","W3D5","W3D6","W3D7","Split","TrD1","TrD2","TrD3","TrD4","TrD5","TrD6","TrD7","TrD8"))
p5 <- ggplot(data=df,mapping=aes(x=Time,y=Score,group=Question,colour=Question))+geom_line()+geom_point()+theme(axis.text.x=element_blank())+scale_y_continuous(limits = c(0, 8))+ggtitle("ID=12, Randomization=3")+facet_wrap(~Question)+geom_vline(xintercept=22)

#6
data6 <- data[c(57:64),]
data6 <- data6[, colSums(is.na(data6)) != nrow(data6)]
data6 <- data6[,-c(1:3)]
x <- rep(NA,8)
data6 <- cbind(data6[,c(1:21)], x, data6[,c(22:29)])
Time <- rep(c("W1D1","W1D2","W1D3","W1D4","W1D5","W1D6","W1D7","W2D1","W2D2","W2D3","W2D4","W2D5","W2D6","W2D7","W3D1","W3D2","W3D3","W3D4","W3D5","W3D6","W3D7","Split","TrD1","TrD2","TrD3","TrD4","TrD5","TrD6","TrD7","TrD8"),8)
Score <- c(t(as.matrix(data6)))
Question <- rep(c("Question1","Question2","Question3","Question4","Question5","Question6","Question7","Question8"),each=30)
df <- data.frame(Time=Time,Score=Score,Question=Question)
df$Time <- factor(df$Time,levels=c("W1D1","W1D2","W1D3","W1D4","W1D5","W1D6","W1D7","W2D1","W2D2","W2D3","W2D4","W2D5","W2D6","W2D7","W3D1","W3D2","W3D3","W3D4","W3D5","W3D6","W3D7","Split","TrD1","TrD2","TrD3","TrD4","TrD5","TrD6","TrD7","TrD8"))
p6 <- ggplot(data=df,mapping=aes(x=Time,y=Score,group=Question,colour=Question))+geom_line()+geom_point()+theme(axis.text.x=element_blank())+scale_y_continuous(limits = c(0, 8))+ggtitle("ID=17, Randomization=3")+facet_wrap(~Question)+geom_vline(xintercept=22)
ggarrange(p3,p4,p5,p6,ncol=2,nrow=2)
```

```{r Fig3, fig.cap="4-week pre-treatment patients",echo=F,warning=F,fig.height=4,fig.width=10}
#Four weeks
#7
data7 <- data[c(25:32),]
data7 <- data7[, colSums(is.na(data7)) != nrow(data7)]
data7 <- data7[,-c(1:3)]
x <- rep(NA,8)
data7 <- cbind(data7[,c(1:28)], x, data7[,c(29:36)])
Time <- rep(c("W1D1","W1D2","W1D3","W1D4","W1D5","W1D6","W1D7","W2D1","W2D2","W2D3","W2D4","W2D5","W2D6","W2D7","W3D1","W3D2","W3D3","W3D4","W3D5","W3D6","W3D7","W4D1","W4D2","W4D3","W4D4","W4D5","W4D6","W4D7","Split","TrD1","TrD2","TrD3","TrD4","TrD5","TrD6","TrD7","TrD8"),8)
Score <- c(t(as.matrix(data7)))
Question <- rep(c("Question1","Question2","Question3","Question4","Question5","Question6","Question7","Question8"),each=37)
df <- data.frame(Time=Time,Score=Score,Question=Question)
df$Time <- factor(df$Time,levels=c("W1D1","W1D2","W1D3","W1D4","W1D5","W1D6","W1D7","W2D1","W2D2","W2D3","W2D4","W2D5","W2D6","W2D7","W3D1","W3D2","W3D3","W3D4","W3D5","W3D6","W3D7","W4D1","W4D2","W4D3","W4D4","W4D5","W4D6","W4D7","Split","TrD1","TrD2","TrD3","TrD4","TrD5","TrD6","TrD7","TrD8"))
p7 <- ggplot(data=df,mapping=aes(x=Time,y=Score,group=Question,colour=Question))+geom_line()+geom_point()+theme(axis.text.x=element_blank())+scale_y_continuous(limits = c(0, 8))+ggtitle("ID=6, Randomization=4")+facet_wrap(~Question)+geom_vline(xintercept=29)

#8
data8 <- data[c(49:56),]
data8 <- data8[,-c(1:3)]
x <- rep(NA,8)
data8 <- cbind(data8[,c(1:28)], x, data8[,c(29:36)])
Time <- rep(c("W1D1","W1D2","W1D3","W1D4","W1D5","W1D6","W1D7","W2D1","W2D2","W2D3","W2D4","W2D5","W2D6","W2D7","W3D1","W3D2","W3D3","W3D4","W3D5","W3D6","W3D7","W4D1","W4D2","W4D3","W4D4","W4D5","W4D6","W4D7","Split","TrD1","TrD2","TrD3","TrD4","TrD5","TrD6","TrD7","TrD8"),8)
Score <- c(t(as.matrix(data8)))
Question <- rep(c("Question1","Question2","Question3","Question4","Question5","Question6","Question7","Question8"),each=37)
df <- data.frame(Time=Time,Score=Score,Question=Question)
df$Time <- factor(df$Time,levels=c("W1D1","W1D2","W1D3","W1D4","W1D5","W1D6","W1D7","W2D1","W2D2","W2D3","W2D4","W2D5","W2D6","W2D7","W3D1","W3D2","W3D3","W3D4","W3D5","W3D6","W3D7","W4D1","W4D2","W4D3","W4D4","W4D5","W4D6","W4D7","Split","TrD1","TrD2","TrD3","TrD4","TrD5","TrD6","TrD7","TrD8"))
p8 <- ggplot(data=df,mapping=aes(x=Time,y=Score,group=Question,colour=Question))+geom_line()+geom_point()+theme(axis.text.x=element_blank())+scale_y_continuous(limits = c(0, 8))+ggtitle("ID=11, Randomization=4")+facet_wrap(~Question)+geom_vline(xintercept=29)
ggarrange(p7,p8,ncol=2,nrow=1)
```

\newpage

## Comment on these EDAs

After analyzing the plots, several noteworthy observations can be made:

1.The score of Q6, which is"Confident in My Ability to Handle Situations" differs from the other questions. While the scores of other questions increase, the score of Q6 decreases.

2.The treatment appears to be ineffective for many questions. For instance, Q8, which is "Physical Feelings in My Body Scare Me" shows no change in trend for six patients. Moreover, the treatment may even worsen the condition, as seen in the first patient's score of Q2, which is "Max Anxiety Today" increased after treatment.

3.Due to the limited dataset consisting of only eight patients with a scoring scale ranging from 0-8, it is challenging to create effective models and it may not be possible to develop highly accurate models. Nevertheless, efforts can be made to create models despite these limitations.

## Methods

By the previous EDA part, we can see the data has some traits.

First, as there are repeated measurements taken for the same individual, there is likely correlation between these measurements. One way to account for this is using a mixed effects model with formula: 

\begin{equation}
    QuestionScore \sim Treat + Time \times Treat + 1 | ID
\end{equation}
		
Second, there are measurements collected over time. Auto-regressive models may be appropriate to account for correlation over time.

\begin{equation}
    QuestionScore_t = \sum_{i=1}^{p} \varphi_i \ast QuestionScore_{t-i} + \varepsilon_i
\end{equation}
		
Third, the question score y is actually ordinal in nature, ranging from 0 to 8. Thus, we can use ordinal regression to account for this.

\begin{equation}
ordered(QuestionScore) \sim Treat + Time \times Ttreat + 1 | ID
\end{equation}


## Result

We fitted separated model for each problems because different problems may have different effect. Even though the respond is ordinal, a linear model may be a useful starting point for modeling because it is easier to interpret and run diagnostics on. The result of most model is same with what we found in EDA, the score of patient is same after making treatment. For instance, in most problem, only the intercept is significant.

```{r, echo=FALSE}
library(knitr)
data1 <- data.frame(
  Row = c("(Intercept)", "T", "t", "T:t"),
  Estimate = c(2.136820, 0.197230, -0.001098, -0.003483),
  Std.Error = c(0.575868, 0.747232, 0.012335, 0.029450),
  df = c(7.9303, 222.20, 221.08, 221.41),
  t_value = c(-28.2, 0.264, -0.089, -0.118),
  Pr_gt_t = c("0.006 **", 0.79206, 0.92916, 0.90596)
)

kable(data1, caption = "Linear Mixed Model for Average Anxiety Today ", col.names = c("Row", "Estimate", "Std. Error", "df", "t value", "Pr(>|t|)"), format = "markdown",
      align = c('c', 'c', 'c', 'c', 'c', 'c'))

```

```{r, echo=FALSE}

#Choose problem
newdata <- data[which(data$Problem=="Average Anxiety Today"),]
newdata <- newdata[,-c(1:3)]
p <- as.matrix(newdata)
y <- c(t(p))
y <- y[!is.na(y)] 
t <- c(1:22,1:29,1:22,1:36,1:29,1:29,1:35,1:29)
T <- c(rep(0,14),rep(1,8),rep(0,21),rep(1,8),rep(0,14),rep(1,8),rep(0,28),rep(1,8),rep(0,21),rep(1,8),rep(0,21),rep(1,8),rep(0,28),rep(1,7),rep(0,21),rep(1,8))
ID <- c(rep(1,22),rep(5,29),rep(3,22),rep(6,36),rep(9,29),rep(12,29),rep(11,35),rep(17,29))
m <- data.frame(y,ID,t,T)
m$y <- as.numeric(y)
```

```{r, echo=FALSE,results='hide'}
model2 <- lmer(y ~ T + t*T + (1 | as.factor(ID)), data = m)
m$y_pred <- fitted(model2)
summary(model2) 
```

```{r, echo=FALSE}
vline_data <- data.frame(ID = c(1,3,5,6,9,11,12,17),  xintercept=c(15,15,22,29,22,29,22,22) )
```

```{r,echo=FALSE,fig.height=4, fig.width=7, fig.cap="Linear Mixed Model for Average Anxiety Today"}
ggplot(m, mapping = aes(x=t, y=y_pred, group=as.factor(ID))) +
  geom_line()+geom_line(aes(x=t, y=y, group=as.factor(ID), colour=as.factor(ID))) +facet_wrap(~ID)+ggtitle("Average Anxiety Today")+geom_vline(data = vline_data, aes(xintercept = xintercept, group = as.factor(ID)), linetype = "dashed")
```

<br> We did the auto-correlation analysis because time is variable in our model. From acf plot, there could be temporal effect. Therefore, we tried to use a time series model, namely an autoregressive (AR) mode. The acf plot almost did not change for each problem. Temporal effect may be too small. <br>

```{r, echo=FALSE,fig.height=4, fig.width=7,fig.cap="ACF Plot of Linear Mixed Model"}
 m$resid <- resid(model2)
acf(m[m$ID==1,]$resid)
```

```{r,include=FALSE}
fm1 <- lme(y ~ T+t*T, random = ~1|as.factor(ID),correlation = corAR1(),data = m)
summary(fm1)
```


```{r,echo=FALSE,fig.height=5, fig.width=8,include=FALSE}
m$resid <- resid(fm1)
acf(m[m$ID==1,]$resid)
```

```{r,echo=FALSE,include=FALSE}
m$y <- as.factor(m$y)
model <- clmm(ordered(y) ~ T + t*T + (1 | as.factor(ID)), data = m)
summary(model)

```

There are only two question the treatment seem to effects to patients, Scares Me when I am Nervous and Confident in My Ability to Handle Situations. However,for Scares Me when I am Nervous and Confident, after using AR models, this effect disappeared. From plot of this question, we could not find significant decreasing of score after taking treatment, which are correspond the result of AR model

```{r,echo=FALSE}
newdata <- data[which(data$Problem=="Scares Me when I am Nervous"),]
newdata <- newdata[,-c(1:3)]
p <- as.matrix(newdata)
y <- c(t(p))
y <- y[!is.na(y)] 
t <- c(1:22,1:29,1:22,1:36,1:29,1:29,1:35,1:29)
T <- c(rep(0,14),rep(1,8),rep(0,21),rep(1,8),rep(0,14),rep(1,8),rep(0,28),rep(1,8),rep(0,21),rep(1,8),rep(0,21),rep(1,8),rep(0,28),rep(1,7),rep(0,21),rep(1,8))
ID <- c(rep(1,22),rep(5,29),rep(3,22),rep(6,36),rep(9,29),rep(12,29),rep(11,35),rep(17,29))
m4 <- data.frame(y,ID,t,T)
m4$y <- as.numeric(y)
```

```{r, echo=FALSE}
new_data <- data.frame(
  Row = c("(Intercept)", "T", "t", "T:t"),
  Estimate = c(2.16590, 2.04479, -0.04548, -0.05264),
  Std.Error = c(0.81736, 0.72973, 0.01204, 0.02874),
  df = c(7.42557, 221.06774, 220.51531, 220.67366),
  t_value = c(2.650, 2.802, -3.778, -1.831),
  Pr_gt_t = c("0.031243 *", "0.005527 **", "0.000203 ***", 0.068379)
)

kable(new_data, caption = "Linear Mixed Model for Scares Me when I am Nervous ", col.names = c("Row", "Estimate", "Std. Error", "df", "t value", "Pr(>|t|)"), format = "markdown",
      align = c('c', 'c', 'c', 'c', 'c', 'c'))
```

```{r, echo=FALSE}
updated_data <- data.frame(
  Row = c("(Intercept)", "T", "t", "T:t"),
  Estimate = c(2.36857845, 1.86567683, -0.05660635, -0.04632292),
  Std.Error = c(0.84549662, 1.06575922, 0.02143659, 0.04515777),
  df = c(220, 220, 220, 220),
  t_value = c(2.801405, 1.750561, -2.640642, -1.025802),
  Pr_gt_t = c("0.005541444**", 0.081415428, "0.008867989**", 0.306111548)
)

kable(updated_data, caption = "Time Series Model for Scares Me when I am Nervous", col.names = c("Row", "Estimate", "Std. Error", "df", "t value", "p-value"), format = "markdown",
      align = c('c', 'c', 'c', 'c', 'c', 'c'))
```

```{r,echo=FALSE, include=FALSE}
fm5 <- lme(y ~ T+t*T, random = ~1|as.factor(ID),correlation = corAR1(),data = m4)
d <- summary(fm5)
d$tTable
```

```{r, echo =FALSE, include=FALSE}
model6 <- lmer(y ~ T+ t*T + (1 | as.factor(ID)), data = m4)
m4$y_pred <- fitted(model6)
summary(model6)
```

```{r,echo=FALSE,fig.height=4, fig.width=7, fig.cap="Linear Mixed Model for Scares Me when I am Nervous"}
ggplot(m4, mapping = aes(x=t, y=y_pred, group=as.factor(ID))) +
  geom_line()+geom_line(aes(x=t, y=y, group=as.factor(ID), colour=as.factor(ID))) +facet_wrap(~ID)+ggtitle("Scares Me when I am Nervous")+geom_vline(data = vline_data, aes(xintercept = xintercept, group = as.factor(ID)), linetype = "dashed")
```

```{r,echo=FALSE,include=FALSE}
m4$resid <- resid(model6)
acf(m4[m4$ID==1,]$resid)
```

```{r,echo=FALSE,include=FALSE}
fm5 <- lme(y ~ T+t*T, random = ~1|as.factor(ID),correlation = corAR1(),data = m4)
d <- summary(fm5)
d$tTable
```

```{r,echo=FALSE,include=FALSE}
m4$resid <- resid(fm5)
acf(m4[m4$ID==1,]$resid)
```

```{r,echo=FALSE,include=FALSE}
m4$y <- as.factor(m4$y)
ordnal4 <- clmm(ordered(y) ~ T+t*T + (1 | as.factor(ID)), data = m4)
summary(ordnal4)
```

The result of Confident in My Ability to Handle Situations is much better than result of Scares Me when I am Nervous. The plot also correspond to result of model. Both T and T:t are significant. Form plot and fitted line, we could find some patient increase after treatment. Finally, we also checked with mixed ordinal model because data is ordinal, but compared with mixed ordinal model is hard to visualize. We put the all result in appendix.

```{r,echo=FALSE,include=FALSE}
newdata <- data[which(data$Problem=="Confident in My Ability to Handle Situations"),]
newdata <- newdata[,-c(1:3)]
p <- as.matrix(newdata)
y <- c(t(p))
y <- y[!is.na(y)] 
t <- c(1:22,1:29,1:22,1:36,1:29,1:29,1:35,1:29)
T <- c(rep(0,14),rep(1,8),rep(0,21),rep(1,8),rep(0,14),rep(1,8),rep(0,28),rep(1,8),rep(0,21),rep(1,8),rep(0,21),rep(1,8),rep(0,28),rep(1,7),rep(0,21),rep(1,8))
ID <- c(rep(1,22),rep(5,29),rep(3,22),rep(6,36),rep(9,29),rep(12,29),rep(11,35),rep(17,29))
m5 <- data.frame(y,ID,t,T)
m5$y <- as.numeric(y)
```

```{r, echo=FALSE}
latest_data <- data.frame(
  Row = c("(Intercept)", "T", "t", "T:t"),
  Estimate = c(3.631392, -2.978075, 0.003036, 0.118754),
  Std.Error = c(0.728410, 0.669260, 0.011040, 0.026362),
  df = c(7.451728, 221.129847, 220.545842, 220.713363),
  t_value = c(4.985, -4.450, 0.275, 4.505),
  Pr_gt_t = c("0.00132 **", "1.36e-05 ***", 0.78354, "1.08e-05 ***")
)

kable(latest_data, caption = "Linear Mixed Model for Confident in My Ability to Handle Situations", col.names = c("Row", "Estimate", "Std. Error", "df", "t value", "Pr(>|t|)"), format = "markdown",
      align = c('c', 'c', 'c', 'c', 'c', 'c'))
```

```{r,echo=FALSE, include=FALSE}
model7 <- lmer(y ~ T+ t*T + (1 | as.factor(ID)), data = m5)
m5$y_pred <- fitted(model7)
summary(model7)
```


```{r, echo=FALSE,fig.height=4, fig.width=7, fig.cap="Linear Mixed Model for Confident in My Ability to Handle Situations"}
ggplot(m5, mapping = aes(x=t, y=y_pred, group=as.factor(ID))) +
  geom_line()+geom_line(aes(x=t, y=y, group=as.factor(ID), colour=as.factor(ID))) +facet_wrap(~ID)+ggtitle("Confident in My Ability to Handle Situations")+geom_vline(data = vline_data, aes(xintercept = xintercept, group = as.factor(ID)), linetype = "dashed")
```

```{r,echo=FALSE,include=FALSE}
m5$resid <- resid(model7)
acf(m5[m5$ID==9,]$resid)
```

```{r,echo=FALSE,include=FALSE}
fm6 <- lme(y ~ T+t*T, random = ~1|as.factor(ID),correlation = corAR1(),data = m5)
summary(fm6)
```

```{r,echo=FALSE,include=FALSE}
m5$resid <- resid(fm6)
acf(m5[m5$ID==9,]$resid)
```

```{r,echo=FALSE,include=FALSE}
m5$y <- as.factor(m5$y)
ordnal5 <- clmm(ordered(y) ~ T+t*T + (1 | as.factor(ID)), data = m5)
summary(ordnal5)
```

```{r,echo=FALSE,include=FALSE}
newdata <- data[which(data$Problem=="Push Away Thoughts and Feelings I Do Not Like"),]
newdata <- newdata[,-c(1:3)]
p <- as.matrix(newdata)
y <- c(t(p))
y <- y[!is.na(y)] 
t <- c(1:22,1:29,1:22,1:36,1:29,1:29,1:35,1:29)
T <- c(rep(0,14),rep(1,8),rep(0,21),rep(1,8),rep(0,14),rep(1,8),rep(0,28),rep(1,8),rep(0,21),rep(1,8),rep(0,21),rep(1,8),rep(0,28),rep(1,7),rep(0,21),rep(1,8))
ID <- c(rep(1,22),rep(5,29),rep(3,22),rep(6,36),rep(9,29),rep(12,29),rep(11,35),rep(17,29))
m6 <- data.frame(y,ID,t,T)
m6$y <- as.numeric(y)
```

# Discussion

One potential confounding feature of the data is that survey questions were answered in privacy before the treatment and in-person in the presence of a therapist during the treatment. This means that differences in pre-treatment and post-treatment responses could be due to the presence of a therapist when answering the survey and not the treatment itself.

One limitation of the mixed effects model is that it assumes a linear relationship between the predictors and the outcome. This assumption may not hold for all problems, and non-linear relationships between the predictors and the outcome may exist. Additionally, the mixed effects model assumes that the effects of the predictors are constant across all individuals, which may not be the case in reality. Furthermore, the number of participants in this study is relatively small, which may limit the power of the mixed effects model to detect significant treatment effects.

Another limitation of the auto-regressive models is that they assume that the correlation between observations decays exponentially over time. This assumption may not hold in all cases, and the correlation may decay at a different rate than the exponential decay assumed by the model. Moreover, the auto-regressive models may be sensitive to outliers and may not perform well in the presence of non-stationarity or non-linear relationships.

Finally, the ordinal regression model assumes a proportional odds assumption, which means that the odds of being in a higher category of the outcome variable are proportional across all levels of the predictors. While there are ways to check this assumption, such as the Brant test, violating the assumption may lead to biased parameter estimates and inaccurate conclusions.

\newpage

## Appendix

```{r,echo=FALSE}
model8 <- lmer(y ~ T+ t*T + (1 | as.factor(ID)), data = m6)
m6$y_pred <- fitted(model8)
summary(model8)
```

```{r,echo=FALSE}
ggplot(m6, mapping = aes(x=t, y=y_pred, group=as.factor(ID))) +
  geom_line()+geom_line(aes(x=t, y=y, group=as.factor(ID), colour=as.factor(ID))) +facet_wrap(~ID)+ggtitle("Push Away Thoughts and Feelings I Do Not Like")+geom_vline(data = vline_data, aes(xintercept = xintercept, group = as.factor(ID)), linetype = "dashed")
```

```{r,echo=FALSE,include=FALSE}
m6$resid <- resid(model8)
acf(m6[m6$ID==9,]$resid)
```

```{r,echo=FALSE}
fm7 <- lme(y ~ T+t*T, random = ~1|as.factor(ID),correlation = corAR1(),data = m6)
summary(fm7)
```

```{r,echo=FALSE,include=FALSE}
m6$resid <- resid(fm7)
acf(m6[m6$ID==9,]$resid)
```

```{r,echo=FALSE}
m6$y <- factor(m6$y, ordered = TRUE)
ordnal6 <- clmm(y ~ T+ t*T + (1 | as.factor(ID)), data = m6)
summary(ordnal6)
```

```{r,echo=FALSE,include=FALSE}
newdata <- data[which(data$Problem=="Physical Feelings in My Body Scare Me"),]
newdata <- newdata[,-c(1:3)]
p <- as.matrix(newdata)
y <- c(t(p))
y <- y[!is.na(y)] 
t <- c(1:22,1:29,1:22,1:36,1:29,1:29,1:35,1:29)
T <- c(rep(0,14),rep(1,8),rep(0,21),rep(1,8),rep(0,14),rep(1,8),rep(0,28),rep(1,8),rep(0,21),rep(1,8),rep(0,21),rep(1,8),rep(0,28),rep(1,7),rep(0,21),rep(1,8))
ID <- c(rep(1,22),rep(5,29),rep(3,22),rep(6,36),rep(9,29),rep(12,29),rep(11,35),rep(17,29))
m7 <- data.frame(y,ID,t,T)
m7$y <- as.numeric(y)
```

```{r,echo=FALSE}
model9 <- lmer(y ~ T+ t*T + (1 | as.factor(ID)), data = m7)
m7$y_pred <- fitted(model9)
summary(model9)
```

```{r,echo=FALSE}
ggplot(m7, mapping = aes(x=t, y=y_pred, group=as.factor(ID))) +
  geom_line()+geom_line(aes(x=t, y=y, group=as.factor(ID), colour=as.factor(ID))) +facet_wrap(~ID)+ggtitle("Push Away Thoughts and Feelings I Do Not Like")+geom_vline(data = vline_data, aes(xintercept = xintercept, group = as.factor(ID)), linetype = "dashed")
```

```{r,echo=FALSE,include=FALSE}
m7$resid <- resid(model9)
acf(m7[m7$ID==1,]$resid)
```

```{r,echo=FALSE}
fm8 <- lme(y ~ T+t*T, random = ~1|as.factor(ID),correlation = corAR1(),data = m7)
summary(fm8)
```

```{r,echo=FALSE,include=FALSE}
m7$resid <- resid(fm8)
acf(m7[m7$ID==1,]$resid)
```

```{r,echo=FALSE}
m7$y <- factor(m7$y, ordered = TRUE)
ordnal7 <- clmm(y ~ T+ t*T + (1 | as.factor(ID)), data = m7)
summary(ordnal7)
```

```{r,echo=FALSE,echo=FALSE,include=FALSE}
newdata <- data[which(data$Problem=="Max Anxiety Today"),]
newdata <- newdata[,-c(1:3)]
p <- as.matrix(newdata)
y <- c(t(p))
y <- y[!is.na(y)] 
t <- c(1:22,1:29,1:22,1:36,1:29,1:29,1:35,1:29)
T <- c(rep(0,14),rep(1,8),rep(0,21),rep(1,8),rep(0,14),rep(1,8),rep(0,28),rep(1,8),rep(0,21),rep(1,8),rep(0,21),rep(1,8),rep(0,28),rep(1,7),rep(0,21),rep(1,8))
ID <- c(rep(1,22),rep(5,29),rep(3,22),rep(6,36),rep(9,29),rep(12,29),rep(11,35),rep(17,29))
m1 <- data.frame(y,ID,t,T)
m1$y <- as.numeric(y)
```

```{r,echo=TRUE,echo=FALSE}
model3 <- lmer(y ~ T + t*T + (1 | as.factor(ID)), data = m1)
m1$y_pred <- fitted(model3)
summary(model3)
```

```{r,echo=FALSE}
ggplot(m1, mapping = aes(x=t, y=y_pred, group=as.factor(ID))) +
  geom_line()+geom_line(aes(x=t, y=y, group=as.factor(ID), colour=as.factor(ID))) +facet_wrap(~ID)+ggtitle("Max Anxiety Today")+geom_vline(data = vline_data, aes(xintercept = xintercept, group = as.factor(ID)), linetype = "dashed")
```

```{r ,echo=FALSE,include=FALSE}
m1$resid <- resid(model3)
acf(m1[m1$ID==1,]$resid)
```

```{r ,echo=FALSE}
fm2 <- lme(y ~ T+t*T, random = ~1|as.factor(ID),correlation = corAR1(),data = m1)
summary(fm2)
```

```{r ,echo=FALSE,include=FALSE}
m1$resid <- resid(fm2) 
acf(m1[m1$ID==1,]$resid)
```

```{r ,echo=FALSE}
m1$y <- as.factor(m1$y)
ordnal1 <- clmm(ordered(y) ~ T+t*T + (1 | as.factor(ID)), data = m1)
summary(ordnal1)
```

```{r ,echo=FALSE,include=FALSE}
newdata <- data[which(data$Problem=="Jump to Negative Conclusions"),]
newdata <- newdata[,-c(1:3)]
p <- as.matrix(newdata)
y <- c(t(p))
y <- y[!is.na(y)] 
t <- c(1:22,1:29,1:22,1:36,1:29,1:29,1:35,1:29)
T <- c(rep(0,14),rep(1,8),rep(0,21),rep(1,8),rep(0,14),rep(1,8),rep(0,28),rep(1,8),rep(0,21),rep(1,8),rep(0,21),rep(1,8),rep(0,28),rep(1,7),rep(0,21),rep(1,8))
ID <- c(rep(1,22),rep(5,29),rep(3,22),rep(6,36),rep(9,29),rep(12,29),rep(11,35),rep(17,29))
m3 <- data.frame(y,ID,t,T)
m3$y <- as.numeric(y)
```

```{r ,echo=FALSE}
model5 <- lmer(y ~ T + t*T + (1 | as.factor(ID)), data = m3)
m3$y_pred <- fitted(model5)
summary(model5)
```

```{r ,echo=FALSE}
ggplot(m3, mapping = aes(x=t, y=y_pred, group=as.factor(ID))) +
  geom_line()+geom_line(aes(x=t, y=y, group=as.factor(ID), colour=as.factor(ID))) +facet_wrap(~ID)+ggtitle("Jump to Negative Conclusions")+geom_vline(data = vline_data, aes(xintercept = xintercept, group = as.factor(ID)), linetype = "dashed")
```

```{r ,echo=FALSE,include=FALSE}
m3$resid <- resid(model5)
acf(m3[m3$ID==11,]$resid)
```

```{r,echo=FALSE}
fm4 <- lme(y ~ T+t*T, random = ~1|as.factor(ID),correlation = corAR1(),data = m3)
b <- summary(fm4)
b$tTable
```

```{r,echo=FALSE,include=FALSE}
m3$resid <- resid(fm4)
acf(m3[m3$ID==11,]$resid)
```

```{r,echo=FALSE}
m3$y <- as.factor(m3$y)
ordnal3 <- clmm(ordered(y) ~ T+t*T + (1 | as.factor(ID)), data = m3)
summary(ordnal3)
```

```{r ,echo=FALSE,include=FALSE}
newdata <- data[which(data$Problem=="Avg Avoidance of Thoughts, Situatoins, Sensations"),]
newdata <- newdata[,-c(1:3)]
p <- as.matrix(newdata)
y <- c(t(p))
y <- y[!is.na(y)] 
t <- c(1:22,1:29,1:22,1:36,1:29,1:29,1:35,1:29)
T <- c(rep(0,14),rep(1,8),rep(0,21),rep(1,8),rep(0,14),rep(1,8),rep(0,28),rep(1,8),rep(0,21),rep(1,8),rep(0,21),rep(1,8),rep(0,28),rep(1,7),rep(0,21),rep(1,8))
ID <- c(rep(1,22),rep(5,29),rep(3,22),rep(6,36),rep(9,29),rep(12,29),rep(11,35),rep(17,29))
m2 <- data.frame(y,ID,t,T)
m2$y <- as.numeric(y)
```

```{r,echo=FALSE}
model4 <- lmer(y ~ T + t*T + (1 | as.factor(ID)), data = m2)
m2$y_pred <- fitted(model4)
summary(model4)
```

```{r ,echo=FALSE}
ggplot(m2, mapping = aes(x=t, y=y_pred, group=as.factor(ID))) +
  geom_line()+geom_line(aes(x=t, y=y, group=as.factor(ID), colour=as.factor(ID))) +facet_wrap(~ID)+ggtitle("Avg Avoidance of Thoughts, Situatoins, Sensations")+geom_vline(data = vline_data, aes(xintercept = xintercept, group = as.factor(ID)), linetype = "dashed")
```

```{r ,echo=FALSE,include=FALSE}
m2$resid <- resid(model4)
acf(m2[m2$ID==11,]$resid)
```

```{r,echo=FALSE}
fm3 <- lme(y ~ T+t*T, random = ~1|as.factor(ID),correlation = corAR1(),data = m2)
a <-summary(fm3)

```

```{r,echo=FALSE,include=FALSE}
m2$resid <- resid(fm3)
acf(m2[m2$ID==11,]$resid)
```

```{r ,echo=FALSE}
m2$y <- as.factor(m2$y)
ordnal2 <- clmm(ordered(y) ~ T+t*T + (1 | as.factor(ID)), data = m2)
summary(ordnal2)
```
